|

### 2021-03-13 documentation/paper.Rmd
Remove reliance on jbmisc functions and download Timeline data remotely

library(PollBasePro)
library(kableExtra)
library(tidyverse)
library(lubridate)
library(tidybayes)
library(patchwork)
library(jbmisc)
library(brms)
library(here)

@@

timeline <-
  readRDS(here("inst", "extdata", "timeline.rds")) %>%
  select(
    date = polldate,
    elecdate,
    country,
    party = partyid,
    vote = poll_
  ) %>%
  filter(country == "United Kingdom") %>% 
  na.omit()

@@

\begin{align*}
Poll_{i} &\sim \mathrm{Normal}(\mu_{i}, \sqrt{\sigma^2 + S_{i}^2}) \srlab{Likelihood function} \\
\mu_{i} &= \alpha_{Day[i]} + \delta_{Pollster[i]} \srlab{Measurement model on $\mu$} \\
\alpha_{t} &= \alpha_{t-1} + \tau \omega_{t-1} \text{ for } t \text{ in } 2, ..., T-1 \srlab{Dynamic model on $\alpha_{t}$} \\
\alpha_{T} &\sim \mathrm{Normal}(\alpha_{T-1}, \tau) \srlab{Adaptive prior on $\alpha_{T}$} \\
\delta_{j} &\sim \mathrm{Normal}(0, 0.1) \text{ for } j \text{ in } 1, ..., J \srlab{Prior on house effects, $\delta$} \\
\omega_{t} &\sim \mathrm{Normal}(0, 0.1) \text{ for } t \text{ in } 1, ..., T-1 \srlab{Prior on random shocks, $\omega$} \\
\tau &\sim \mathrm{Normal}(0, 0.05)^{+} \srlab{Positive prior on scale of innovations, $\tau$} \\
\sigma &\sim \mathrm{Exponential}(20) \srlab{Prior on residual error, $\sigma$} \\
\end{align*}

@@

tl <-
  readRDS(here("inst", "extdata", "timeline.rds")) %>%
  select(
    date = polldate,
    elecdate,
    country,
    party = partyid,
    vote = poll_
  ) %>%
  filter(country == "United Kingdom") %>%
  mutate(
    vote = vote/100,
    party = case_when(party == 1 ~ "con", party == 2 ~ "lab", party == 3 ~ "lib"),
    polldate = as_date(date)
  ) %>%
  na.omit()

@@

timeplot <- 
pbp_long %>%
  ggplot(
    aes(
      x = date,
      y = est,
      ymin = est - qnorm(0.975)*err,
      ymax = est + qnorm(0.975)*err,
      colour = party,
      fill = party
    )
  ) +
  geom_ribbon(alpha = .3, colour = NA) +
  geom_line() +
  coord_cartesian(ylim = c(0, 0.62)) +
  scale_colour_manual(values = pty_cols) +
  scale_fill_manual(values = pty_cols) +
  scale_y_continuous(
    breaks = seq(0, .6, by = .1),
    labels = scales::percent_format(accuracy = 1)
    ) +
  scale_x_date(
    breaks = seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "5 years"),
    labels = year(seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "5 years"))
    ) +
  jbmisc::theme_bailey() +
  labs(
    colour = "Party",
    fill = "Party",
    y = "Vote Share"
  ) +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    axis.title.x = element_blank()
  )

>>>>

library(PollBasePro)
library(kableExtra)
library(tidyverse)
library(lubridate)
library(tidybayes)
library(patchwork)
library(brms)
library(here)

@@

timeline <-
  load_timeline() %>%
  select(
    date = polldate,
    elecdate,
    country,
    party = partyid,
    vote = poll_
  ) %>%
  filter(country == "United Kingdom") %>% 
  na.omit()

@@

\begin{align*}
Poll_{i} &\sim \mathrm{Normal}(\mu_{i}, \sqrt{\sigma^2 + S_{i}^2}) \srlab{Likelihood function} \\
\mu_{i} &= \alpha_{Day[i]} + \delta_{Pollster[i]} \srlab{Measurement model on $\mu$} \\
\alpha_{t} &= \alpha_{t-1} + \tau \omega_{t-1} \text{ for } t \text{ in } 2, ..., T-1 \srlab{Dynamic model on $\alpha_{t}$} \\
\alpha_{T} &\sim \mathrm{Normal}(\alpha_{T-1}, \tau) \srlab{Adaptive prior on $\alpha_{T}$} \\
\delta_{j} &\sim \mathrm{Normal}(0, 0.05) \text{ for } j \text{ in } 1, ..., J \srlab{Prior on house effects, $\delta$} \\
\omega_{t} &\sim \mathrm{Normal}(0, 0.1) \text{ for } t \text{ in } 1, ..., T-1 \srlab{Prior on random shocks, $\omega$} \\
\tau &\sim \mathrm{Normal}(0, 0.05)^{+} \srlab{Positive prior on scale of innovations, $\tau$} \\
\sigma &\sim \mathrm{Exponential}(20) \srlab{Prior on residual error, $\sigma$} \\
\end{align*}

@@

tl <-
  load_timeline() %>%
  select(
    date = polldate,
    elecdate,
    country,
    party = partyid,
    vote = poll_
  ) %>%
  filter(country == "United Kingdom") %>%
  mutate(
    vote = vote/100,
    party = case_when(party == 1 ~ "con", party == 2 ~ "lab", party == 3 ~ "lib"),
    polldate = as_date(date)
  ) %>%
  na.omit()

@@

timeplot <- 
pbp_long %>%
  ggplot(
    aes(
      x = date,
      y = est,
      ymin = est - qnorm(0.975)*err,
      ymax = est + qnorm(0.975)*err,
      colour = party,
      fill = party
    )
  ) +
  geom_ribbon(alpha = .3, colour = NA) +
  geom_line() +
  coord_cartesian(ylim = c(0, 0.62)) +
  scale_colour_manual(values = pty_cols) +
  scale_fill_manual(values = pty_cols) +
  scale_y_continuous(
    breaks = seq(0, .6, by = .1),
    labels = scales::percent_format(accuracy = 1)
    ) +
  scale_x_date(
    breaks = seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "5 years"),
    labels = year(seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "5 years"))
    ) +
   theme_minimal() +
    theme(
      legend.position = "bottom",
      legend.title = element_blank(),
      text = element_text(family = "Cabin", color = "black", size = 8),
      plot.title = element_text(family = "Cabin", face = "bold", size = rel(1.4), hjust = 0),
      plot.subtitle = element_text(family = "Cabin", size = rel(1), hjust = 0, margin = margin(b = 10)),
      axis.line = element_line(lineend = "round"),
      axis.title.x = element_blank(),
      axis.text.x = element_text(color = "black", size = rel(1)),
      axis.ticks.x = element_line(lineend = "round"),
      axis.title.y = element_text(family = "Cabin", face = "bold", size = rel(1)),
      axis.text.y = element_text(color = "black", size = rel(1)),
      strip.text = element_text(family = "Cabin", face = "bold", size = rel(1)),
      panel.spacing = unit(.3, "cm"),
      panel.grid.major.y = element_line(size = .5, lineend = "round"),
      panel.grid.minor.y = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
    ) +
  labs(
    colour = "Party",
    fill = "Party",
    y = "Vote Share"
  )

### 2021-03-13 documentation/readme.Rmd
Remove reliance on jbmisc functions and download Timeline data remotely

timeplot <- 
pollbasepro %>% 
  pivot_longer(
    cols = c(-date, -election, -govt, -week, -month, -quarter, -year, -con_ldr, -lab_ldr, -lib_ldr),
    names_to = c("party", ".value"),
    names_sep = "_",
  ) %>%
  mutate(
    party =
      case_when(
        party == "con" ~ "Conservative Party",
        party == "lab" ~ "Labour Party",
        party == "lib" ~ "Liberals (Various Forms)"
      ) %>% 
      factor(
        levels = 
          c("Conservative Party",
            "Labour Party",
            "Liberals (Various Forms)"
          )
      )
  ) %>%
  ggplot(
    aes(
      x = date,
      y = est,
      ymin = est - qnorm(0.975)*err,
      ymax = est + qnorm(0.975)*err,
      colour = party,
      fill = party
    )
  ) +
  geom_ribbon(alpha = .3, colour = NA) +
  geom_line() +
  scale_colour_manual(values = pty_cols) +
  scale_fill_manual(values = pty_cols) +
  scale_y_continuous(
    breaks = seq(0, .6, by = .1),
    labels = scales::percent_format(accuracy = 1)
    ) +
  scale_x_date(
    breaks = seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"),
    labels = format(seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"), "%b %y")
    ) +
  coord_cartesian(
    ylim = c(0, 0.62),
    xlim = c(as_date("2019-12-12"), Sys.Date())
    ) +
  jbmisc::theme_bailey() +
  labs(
    title = paste0("British Poll of Polls, ", str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")),
    colour = "Party",
    fill = "Party",
    y = "Vote Share",
    caption = "Based on data from PollBasePro, created by @PoliSciJack, @markpack, and @mansillo: www.github.com/jackobailey/PollBasePro"
  ) +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    axis.title.x = element_blank()
  )

>>>>

timeplot <- 
pollbasepro %>% 
  pivot_longer(
    cols = c(-date, -election, -govt, -week, -month, -quarter, -year, -con_ldr, -lab_ldr, -lib_ldr),
    names_to = c("party", ".value"),
    names_sep = "_",
  ) %>%
  mutate(
    party =
      case_when(
        party == "con" ~ "Conservative Party",
        party == "lab" ~ "Labour Party",
        party == "lib" ~ "Liberals (Various Forms)"
      ) %>% 
      factor(
        levels = 
          c("Conservative Party",
            "Labour Party",
            "Liberals (Various Forms)"
          )
      )
  ) %>%
  ggplot(
    aes(
      x = date,
      y = est,
      ymin = est - qnorm(0.975)*err,
      ymax = est + qnorm(0.975)*err,
      colour = party,
      fill = party
    )
  ) +
  geom_ribbon(alpha = .3, colour = NA) +
  geom_line() +
  scale_colour_manual(values = pty_cols) +
  scale_fill_manual(values = pty_cols) +
  scale_y_continuous(
    breaks = seq(0, .6, by = .1),
    labels = scales::percent_format(accuracy = 1)
    ) +
  scale_x_date(
    breaks = seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"),
    labels = format(seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"), "%b %y")
    ) +
  coord_cartesian(
    ylim = c(0, 0.62),
    xlim = c(as_date("2019-12-12"), Sys.Date())
    ) +
  theme_minimal() +
    theme(
      legend.position = "bottom",
      legend.title = element_blank(),
      text = element_text(family = "Cabin", color = "black", size = 8),
      plot.title = element_text(family = "Cabin", face = "bold", size = rel(1.4), hjust = 0),
      plot.subtitle = element_text(family = "Cabin", size = rel(1), hjust = 0, margin = margin(b = 10)),
      axis.line = element_line(lineend = "round"),
      axis.title.x = element_blank(),
      axis.text.x = element_text(color = "black", size = rel(1)),
      axis.ticks.x = element_line(lineend = "round"),
      axis.title.y = element_text(family = "Cabin", face = "bold", size = rel(1)),
      axis.text.y = element_text(color = "black", size = rel(1)),
      strip.text = element_text(family = "Cabin", face = "bold", size = rel(1)),
      panel.spacing = unit(.3, "cm"),
      panel.grid.major.y = element_line(size = .5, lineend = "round"),
      panel.grid.minor.y = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
    ) +
  labs(
    title = paste0("British Poll of Polls, ", str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")),
    colour = "Party",
    fill = "Party",
    y = "Vote Share",
    caption = "Based on data from PollBasePro, created by @PoliSciJack, @markpack, and @mansillo: www.github.com/jackobailey/PollBasePro"
  )

### 2021-03-13 documentation/userguide.Rmd
Add data DOI
Remove reliance on jbmisc functions and download Timeline data remotely

library(PollBasePro)
library(kableExtra)
library(tidyverse)
library(lubridate)
library(jbmisc)
library(brms)
library(here)

@@

ggplot() +
  geom_density_2d(
    data = pollbasepro %>% mutate(facet = "Conservative"),
    mapping = 
      aes(
        x = date,
        y = qnorm(.975)*con_err
        ),
    colour = "#0087dc",
    alpha = .4
  ) +
  stat_smooth(
    data = pollbasepro %>% mutate(facet = "Conservative"),
    mapping = aes(
      x = date,
      y = qnorm(.975)*con_err
    ),
    method = "lm",
    formula = y ~ x,
    se = TRUE,
    colour = "black"
  ) +
  geom_density_2d(
    data = pollbasepro %>% mutate(facet = "Labour"),
    mapping = 
      aes(
        x = date,
        y = qnorm(.975)*lab_err
        ),
    colour = "#d50000",
    alpha = .4
  ) +
  stat_smooth(
    data = pollbasepro %>% mutate(facet = "Labour"),
    mapping = aes(
      x = date,
      y = qnorm(.975)*lab_err
    ),
    method = "lm",
    formula = y ~ x,
    se = TRUE,
    colour = "black"
  ) +
  geom_density_2d(
    data = pollbasepro %>% mutate(facet = "Liberal"),
    mapping = 
      aes(
        x = date,
        y = qnorm(.975)*lib_err
        ),
    colour = "#fdbb30",
    alpha = .4
  ) +
  stat_smooth(
    data = pollbasepro %>% mutate(facet = "Liberal"),
    mapping = aes(
      x = date,
      y = qnorm(.975)*lib_err
    ),
    method = "lm",
    formula = y ~ x,
    se = TRUE,
    colour = "black"
  ) +
  facet_wrap(~facet) +
  scale_y_continuous(
    breaks = seq(0, 0.05, by = .01),
    labels = scales::percent_format(suffix = "pts", accuracy = .1)
  ) +
  scale_x_date(
    breaks = seq.Date(as.Date("1960-01-01"), as.Date("2020-01-01"), by = "10 years"),
    labels = year(seq.Date(as.Date("1960-01-01"), as.Date("2020-01-01"), by = "10 years"))
  ) +
  coord_cartesian(ylim = c(0, 0.05)) +
  jbmisc::theme_bailey() +
  labs(y = "Posterior Uncertainty (95%)") +
  theme(axis.title.x = element_blank())

@@

samplesizes %>%
  ggplot(
    aes(
      x = date,
      y = n_est,
      ymin = qpois(0.025, n_est),
      ymax = qpois(0.975, n_est)
    )
  ) +
  geom_ribbon(alpha = .3, colour = NA) +
  geom_line() +
  scale_y_continuous(breaks = seq(0, 2500, by = 500)) +
  scale_x_date(
    breaks = seq.Date(as.Date("1945-01-01"), as.Date("2020-01-01"), by = "5 years"),
    labels = year(seq.Date(as.Date("1945-01-01"), as.Date("2020-01-01"), by = "5 years"))
    ) +
  coord_cartesian(ylim = c(0, 2600)) +
  jbmisc::theme_bailey() +
  labs(
    y = "Imputed Sample Size"
  ) +
  theme(axis.title.x = element_blank())

>>>>

library(PollBasePro)
library(kableExtra)
library(tidyverse)
library(lubridate)
library(brms)
library(here)

@@

ggplot() +
  geom_density_2d(
    data = pollbasepro %>% mutate(facet = "Conservative"),
    mapping = 
      aes(
        x = date,
        y = qnorm(.975)*con_err
        ),
    colour = "#0087dc",
    alpha = .4
  ) +
  stat_smooth(
    data = pollbasepro %>% mutate(facet = "Conservative"),
    mapping = aes(
      x = date,
      y = qnorm(.975)*con_err
    ),
    method = "lm",
    formula = y ~ x,
    se = TRUE,
    colour = "black"
  ) +
  geom_density_2d(
    data = pollbasepro %>% mutate(facet = "Labour"),
    mapping = 
      aes(
        x = date,
        y = qnorm(.975)*lab_err
        ),
    colour = "#d50000",
    alpha = .4
  ) +
  stat_smooth(
    data = pollbasepro %>% mutate(facet = "Labour"),
    mapping = aes(
      x = date,
      y = qnorm(.975)*lab_err
    ),
    method = "lm",
    formula = y ~ x,
    se = TRUE,
    colour = "black"
  ) +
  geom_density_2d(
    data = pollbasepro %>% mutate(facet = "Liberal"),
    mapping = 
      aes(
        x = date,
        y = qnorm(.975)*lib_err
        ),
    colour = "#fdbb30",
    alpha = .4
  ) +
  stat_smooth(
    data = pollbasepro %>% mutate(facet = "Liberal"),
    mapping = aes(
      x = date,
      y = qnorm(.975)*lib_err
    ),
    method = "lm",
    formula = y ~ x,
    se = TRUE,
    colour = "black"
  ) +
  facet_wrap(~facet) +
  scale_y_continuous(
    breaks = seq(0, 0.05, by = .01),
    labels = scales::percent_format(suffix = "pts", accuracy = .1)
  ) +
  scale_x_date(
    breaks = seq.Date(as.Date("1960-01-01"), as.Date("2020-01-01"), by = "10 years"),
    labels = year(seq.Date(as.Date("1960-01-01"), as.Date("2020-01-01"), by = "10 years"))
  ) +
  coord_cartesian(ylim = c(0, 0.05)) +
   theme_minimal() +
    theme(legend.title = element_text(family = "Cabin", face = "bold", size = rel(1)),
                   text = element_text(family = "Cabin", color = "black", size = 8),
                   plot.title = element_text(family = "Cabin", face = "bold", size = rel(1.4), hjust = 0),
                   plot.subtitle = element_text(family = "Cabin", size = rel(1), hjust = 0, margin = margin(b = 10)),
                   axis.line = element_line(lineend = "round"),
                   axis.title.x = element_blank(),
                   axis.text.x = element_text(color = "black", size = rel(1)),
                   axis.ticks.x = element_line(lineend = "round"),
                   axis.title.y = element_text(family = "Cabin", face = "bold", size = rel(1)),
                   axis.text.y = element_text(color = "black", size = rel(1)),
                   strip.text = element_text(family = "Cabin", face = "bold", size = rel(1)),
                   panel.spacing = unit(.3, "cm"),
                   panel.grid.major.y = element_line(size = .5, lineend = "round"),
                   panel.grid.minor.y = element_blank(),
                   panel.grid.major.x = element_blank(),
                   panel.grid.minor.x = element_blank()
    ) +
  labs(y = "Posterior Uncertainty (95%)")

@@

samplesizes %>%
  ggplot(
    aes(
      x = date,
      y = n_est,
      ymin = qpois(0.025, n_est),
      ymax = qpois(0.975, n_est)
    )
  ) +
  geom_ribbon(alpha = .3, colour = NA) +
  geom_line() +
  scale_y_continuous(breaks = seq(0, 2500, by = 500)) +
  scale_x_date(
    breaks = seq.Date(as.Date("1945-01-01"), as.Date("2020-01-01"), by = "5 years"),
    labels = year(seq.Date(as.Date("1945-01-01"), as.Date("2020-01-01"), by = "5 years"))
    ) +
  coord_cartesian(ylim = c(0, 2600)) +
  theme_minimal() +
    theme(legend.title = element_text(family = "Cabin", face = "bold", size = rel(1)),
                   text = element_text(family = "Cabin", color = "black", size = 8),
                   plot.title = element_text(family = "Cabin", face = "bold", size = rel(1.4), hjust = 0),
                   plot.subtitle = element_text(family = "Cabin", size = rel(1), hjust = 0, margin = margin(b = 10)),
                   axis.line = element_line(lineend = "round"),
                   axis.title.x = element_blank(),
                   axis.text.x = element_text(color = "black", size = rel(1)),
                   axis.ticks.x = element_line(lineend = "round"),
                   axis.title.y = element_text(family = "Cabin", face = "bold", size = rel(1)),
                   axis.text.y = element_text(color = "black", size = rel(1)),
                   strip.text = element_text(family = "Cabin", face = "bold", size = rel(1)),
                   panel.spacing = unit(.3, "cm"),
                   panel.grid.major.y = element_line(size = .5, lineend = "round"),
                   panel.grid.minor.y = element_blank(),
                   panel.grid.major.x = element_blank(),
                   panel.grid.minor.x = element_blank()
    ) +
  labs(
    y = "Imputed Sample Size"
  )
